---
title: "Rodillas FA 7"
output: github_document
date: "2024-02-29"
---
1. With lambda = 4 per minute, we can obtain the probability based on time 
```{r}
#1. With lambda = 4 per minute, we can obtain the probability based on time 
lambda1 <- 4  

#at most 15
p_at_15 <- 1 -exp(-lambda1/60 * 0.25)
cat("P(T ≤ 0.25) =", p_at_15 *100, "% \n")

# greater than 30
p_more_30 <- exp(-lambda1/60 * 0.5)
cat("P(T > 0.5) =",p_more_30 *100, "%\n")

# 15 to a minute
p_15_60 <- exp(-lambda1/60 * 0.25) - exp(-lambda1/60 * 1)
cat("P(0.25 < T < 1) =",p_15_60 *100, "%\n")

```



3. average job comp center is 2 per minute, with Poisson

```{r}
#Using the ppois

# aveage rate job per min
lambda2 <- 2 

# (a) more than 2 jobs, 1 min
p_2_in_1 <- 1 - ppois(2, lambda2)
cat("The probability of having more than 2 jobs in one minute: ",p_2_in_1 *100, "% \n")

# (b) 30 sec interval, 2 jobs
p_30_between_2 <- ppois(1, lambda2/2)
cat("The probability of having an interval of at least 30 seconds in two jobs: ",p_30_between_2 *100, "%\n")

# less than 30 sec interval, 2 jobs
p_30less_between_2 <- 1 -p_30_between_2
cat("The probability of having less than 30 seconds interval in two jobs: ",p_30less_between_2 *100, "%\n")

# (d) job after 30, where 30 has no job
p_30_after_30 <- 1 - exp(-lambda2/2)
cat("The probability that a job will arrive in the next 30 seconds, after 30 seconds of nothing: ", p_30_after_30 *100, "%\n")

```



7. With an ave of 15 visits per hr, using Poisson, find the probability
```{r}
#7. With an ave of 15 visits per hr, using Poisson, find the probability 

lambda3 <- 15

# (a) 10 minutes will elapse without a visit
lambda_min <- lambda3/6 #since 1 hr has 60 mins, divide the time per 10 mins
p_novisit_10 <- ppois(0, lambda_min) 
cat("The probability that at least 10 minutes will elapse without a visit: ",  p_novisit_10 *100, "% \n")

# (b) ! hr, <8 visits 
p_hour_lessthan8 <- ppois(7, lambda3)
cat("Probability that in any hour, there will be less than eight visits: ",p_hour_lessthan8 *100, "% \n")

# (c)A visit after 15 mins, where 15 have elapsed
lambda_min2 <- lambda3/4 #convert hour. With 60 mins / 4 is 15 mins
p_15_after_15 <- 1 - ppois(0, lambda_min2)  
cat("Probability that a visit will occur in the next 15 minutes:", p_15_after_15 *100, "% \n")

# (d) top quartile
top_quartile <- qpois(0.75, lambda3)
cat("Top quartile (number of visits):", top_quartile)
```

The top quartile represents the top 75% of data falls under. In the case of this problem, the top quartile are the number of visits which falls under the time elapsed. In this case, there are 18 visits per hour in the top quartile, meaning that 75% of the time, there are 5 visits or lower in the website.  